Eliminating prior-bias from sparse-projection tomographic reconstructions

### 2020-07-23 paper/response.tex

\begin{table}[!h]
  \centering
\caption{Computation time for reconstruction of volumes using various methods. The configuration of the system used was x86\_64 architecture, 62GB RAM, 12-core AMD 3.8GHz processor, with Nvidia GeForce RTX 2080 Ti GPU.}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}c@{}}Spatially-\\Varying\\ prior \\+ l1-ls\end{tabular}} \\\hline
%\textbf{\begin{tabular}[c]{@{}c@{}}Potato\\size:(150,150,100)\\45 views\end{tabular}}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338$\times$338$\times$123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130$\times$130$\times$130)\\xx views\end{tabular}}  & 6 sec. & 3 hrs. & 60 min. &  17 hrs.\\ \hline
\end{tabular}
\label{table:Computation_time_3D}
\end{table}

The computation time for each of the methods is presented in Table~\ref{table:Computation_time_3D}. For spatially-varying prior, most of the computation time is used in the generation of low-quality eigen-space by reconstructing  each of the templates using CS and FDK. This process cannot be performed offline as it involves applying the same imaging geometry used for scanning the test. We had performed these reconstructions sequentially. Ideally, these reconstructions must be performed in parallel on different machines to significantly reduce the computation time.\\

@@

\textbf{Response:} In this work, we do not consider low-dose settings. Here, we have used standard-dose radiation and hence the Poisson noise (that is present in low-dose measurements) is minimal here. We observed this consistently in all the real datasets which we experimented with. The only significant reconstruction artefacts are the ones due to insufficient views, and we have focussed on removing these alone, whilst preserving the new changes.
For the case of low-dose imaging, we have presented a few reconstruction techniques in~\cite{gopal2019low}.\\

\textcolor{blue}{\textbf{R3-C14:}\textit{The paper includes several statements that are either false or not well supported. Examples include:    - `Fig. 1 shows that although CS removes the artefacts created due to subsampling, its reconstruction is blurred.' This is a very broad statement about the performance of an entire group of methods (CS), for which giving only a single image without any details is not enough support by far.}}

\textbf{Response:} We wish to point out that our inference about CS reconstructions being blurred on undersampled data has been earlier pointed out in the published work~\cite{PICCS} in Page 4, line 22.  We again reiterate this here that the reconstruction using CS is of good quality (as proven in literature) when the number of views is large. However, when the number of views is limited, the optimizer (with optimal lambda) indeed blurs the overall reconstruction in an attempt to remove the sub-sampling artefacts. We have now demonstrated this in our response to \textbf{R3-C7}.

However, for greater clarity about our comments on CS, we have retracted the generic statement from our earlier Introduction section. (``Fig. 1 shows that although CS removes the artefacts created due to subsampling, its reconstruction is blurred.''). Instead, since we have used a particular optimizer of the CS family, namely the l1-regularized least squares (l1-ls), we have now rephrased the term `CS'  with `l1-ls' wherever appropriate in the paper.\\
